%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Academic Experiences}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Master Thesis (with Prof. Dr. Torsten Hoefler)} % Job title
    {Scalable Parallel Computing Lab (SPCL) @ ETH Z\"urich} % Organization
    {Z\"urich, Switzerland} % Location
    {Mar. 2023 - Sept. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed FPsPIN, a FPGA-based prototype system for sPIN}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Semester Project (with Prof. Dr. Timothy Roscoe)} % Job title
    {NetOS, Systems Group @ ETH Z\"urich} % Organization
    {Z\"urich, Switzerland} % Location
    {Oct. 2022 - Feb. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and developed the Enzian Firmware Resource Interface (EFRI)}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Undergraduate Research (with Prof. Yun Liang)} % Job title
    {Center for Energy-efficient Computing and Applications (CECA) @ PKU} % Organization
    {Beijing, China} % Location
    {Dec. 2017 - Jul. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Build heterogeneous RISC-V SoCs that foster state-of-the-art accelerator designs}
        \item {Explore performance and efficiency of emerging platforms with HW/SW Co-design}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Intern (with Prof. Babak Falsafi)} % Job title
    {Parallel Systems Architecture Lab (PARSA) @ EPFL} % Organization
    {Lausanne, Switzerland (remote)} % Location
    {Jul. 2020 - Jan. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Design next-generation memory subsystems targeting terabyte-scale situations}
        \item {Build RISC-V-based hardware and software solutions for validation}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Academic Collaboration (with Prof. Chenren Xu \& Dr. Pengyu Zhang)} % Job title
    {XG Lab @ Alibaba DAMO Academy} % Organization
    {Beijing, China} % Location
    {Sept. 2020 - Jan. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Build high-speed FPGA receiver for high-accuracy UHF RFID localization system}
        \item {Interface with RF frontends with RISC-V MCU and host over PCIe}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Team Leader} % Job title
    {PKU Student Supercomputing Competition Team (PKUSC)} % Organization
    {Beijing, China} % Location
    {Nov. 2017 - Nov. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Optimize real-world HPC benchmarks and applications for performance and efficiency}
        \item {Gain profound experience in cluster building, management, and maintenance}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}

\cvsection{Work Experiences}

\begin{cventries}
    \cventry
    {Research Intern}
    {SenseTime}
    {Beijing, China}
    {Jun. 2019 - Dec. 2019}
    {
        \begin{cvitems}
        \item {Design and develop in-house GPU deep learning compiler framework}
        \item {Awarded \textit{Outstanding Intern} title}
        \end{cvitems}
    }
\end{cventries}

\cvsection{Teaching Experiences}

\begin{cventries}
    \cventry
    {Hilfsassistenz (HA)}
    {Advanced Operating Systems, ETH Z\"urich}
    {Z\"urich, Switzerland}
    {Mar. 2022 - Aug. 2023}
    {}

    \cventry
    {Hilfsassistenz (HA)}
    {Computer Systems, ETH Z\"urich}
    {Z\"urich, Switzerland}
    {Sept. 2022 - Feb. 2023}
    {}

    \cventry
    {Teaching Assistant (TA)}
    {Computer Networks (Honor Track), Peking University}
    {Beijing, China}
    {Sept. 2020 - Feb. 2021}
    {}
\end{cventries}
