%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------

\cvsection{Publications}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {The ACM SIGOPS Workshop on Hot Topics in Operating Systems (HotOS)}
    {{\normalfont \textbf{Pengcheng Xu}, Timothy Roscoe. ``The NIC should be part of the OS.''}}
    {Banff, Alberta, Canada} % Location
    {May 2025} % Date(s)
    {}

%---------------------------------------------------------
  \cventry
    {arXiv}
    {{\normalfont Anastasiia Ruzhanskaia, \textbf{Pengcheng Xu}, David Cock, Timothy Roscoe. ``Rethinking Programmed I/O for Fast Devices, Cheap Cores, and Coherent Interconnects''}}
    {Online} % Location
    {Oct.\ 2024} % Date(s)
    {}

%---------------------------------------------------------
  \cventry
    {arXiv}
    {{\normalfont Timo Schneider, \textbf{Pengcheng Xu}, Torsten Hoefler. ``FPsPIN: An FPGA-based Open-Hardware Research Platform for Processing in the Network''}}
    {Online} % Location
    {May.\ 2024} % Date(s)
    {}

%---------------------------------------------------------
  \cventry
    {ETH Library}
    {{\normalfont \textbf{Pengcheng Xu}. ``Full-System Evaluation of the sPIN In-Network-Compute Architecture''}}
    {ETH Zurich} % Location
    {Sept.\ 2023} % Date(s)
    {}

%---------------------------------------------------------
  \cventry
    {ETH Library}
    {{\normalfont \textbf{Pengcheng Xu}. ``Enzian Firmware Resource Interface''}}
    {ETH Zurich} % Location
    {Feb.\ 2023} % Date(s)
    {}

%---------------------------------------------------------
  \cventry
    {IEEE Transactions on Parallel and Distributed Systems (TPDS)}
    {{\normalfont Zejia Fan, Yuchen Gu, Zhewen Hao, Yueyang Pan, \textbf{Pengcheng Xu}, Yuxuan Yan, Fangyuan Yang, Zhenxin Fu, Yun Liang. ``Critique of `MemXCT: Memory-Centric X-Ray CT Reconstruction With Massive Parallelization' by SCC Team From Peking University''}}
    {Journal} % Location
    {Jan.\ 2022} % Date(s)
    {}

%---------------------------------------------------------
  \cventry
    {International Symposium on Computer Architecture (ISCA)}
    {{\normalfont Qingcheng Xiao, Size Zheng, Bingzhe Wu, \textbf{Pengcheng Xu}, Xuehai Qian, Yun Liang. ``HASCO: Towards Agile HArdware and Software CO-design for Tensor Computation''}}
    {Worldwide} % Location
    {June 2021} % Date(s)
    {}

%---------------------------------------------------------
  \cventry
    {IEEE Transactions on Parallel and Distributed Systems (TPDS)}
    {{\normalfont Yihua Cheng, Zejia Fan, Jing Mai, Yifan Wu, \textbf{Pengcheng Xu}, Yuxuan Yan, Zhenxin Fu, Yun Liang. ``Critique of `Planetary Normal Mode Computation: Parallel Algorithms, Performance, and Reproducibility' by SCC Team From Peking University''}}
    {Journal} % Location
    {Jan.\ 2021} % Date(s)
    {}

%---------------------------------------------------------
  \cventry
    {Workshop on Computer Architecture Research with RISC-V (CARRV), co-located with ISCA} % Role
    {{\normalfont \textbf{Pengcheng Xu}, Yun Liang. ``Automatic Code Generation for Rocket Chip RoCC Accelerators''}} % Event
    {Virtual Workshop} % Location
    {May 2020} % Date(s)
    {}
\end{cventries}

\cvsection{Posters}
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {European Conference on Computer Systems (EuroSys)}
    {{\normalfont \textbf{Pengcheng Xu}, Jasmin Schult, Zikai Liu, Roman Meier, Timothy Roscoe. ``Lauberhorn: a Smart NIC that is part of the OS''}}
    {Rotterdam, the Netherlands} % Location
    {Apr.\ 2025} % Date(s)
    {}

%---------------------------------------------------------
  \cventry
    {USENIX Symposium on Operating Systems Design and Implementation (OSDI)}
    {{\normalfont \textbf{Pengcheng Xu}, Jasmin Schult, Anastasiia Ruzhanskaia, David Cock, Timothy Roscoe. ``Enzian fast RPC: merging OS and NIC on coherent interconnects''}}
    {Santa Clara, CA, USA} % Location
    {Aug.\ 2024} % Date(s)
    {}

\end{cventries}
